Test-driven Knowledge Graph Construction

### 2023-05-06 doc/paper4.tex
Remove categories of CQs

\textbf{Step 1:} The first step of the proposed method is gathering user requirements. We started with capturing user requirements formulated as CQs, such as \textit{"What is the sensitivity of given tests according to their manufacturers?"} We came up with 19 CQs in total, divided into two categories based on their objectives. The first category of questions asked what information should be present in the knowledge graph, the second category included analytical questions. The complete list of the CQs is available online.\footnote{\url{https://github.com/KIZI/antigen-covid-tests-knowledge-graph/wiki/Competency-questions}}

>>>>

\textbf{Step 1:} The first step of the proposed method is gathering user requirements. We started with capturing user requirements formulated as CQs, such as \textit{"What is the sensitivity of given tests according to their manufacturers?"} We came up with 19 CQs in total, covering basic information look-up and more complex analytical questions. The complete list of the CQs is available online.\footnote{\url{https://github.com/KIZI/antigen-covid-tests-knowledge-graph/wiki/Competency-questions}}
